Hydras \& Co.

### 2023-07-12 doc/chapter-natural-deduction.tex
work on chapter-natural-deduction

@@

\begin{project}[**]
  The type \texttt{SysPrf} has sort \texttt{Prop}, which prevent us from
extracting the underlying proof tree and its fringe from an hypothesis 
of the form $X\sdash f$. 
It would be nice (\emph{e.g.} for a better understanding of the proof of the deduction theorem) to be able to compute the  proof-tree built
by the proof of the deduction lemma. 
On a fresh branch of the project, please change the definition of
\texttt{SysPrf} and fix the errors this change could cause in the rest of the files. 
\end{project}

@@

>>>>

The \emph{rule of implication elimination} is derived from \texttt{Prf}'s 
\emph{modus ponens} \texttt{MP}.  Since all elements of the fringe 
\texttt{x} [resp. \texttt{x1}] of the proof tree \texttt{px} [resp. \texttt{px1}] belong to T, so are the elements of the fringe \texttt{x++x1} of
(\texttt{MP \dots{}  px px1}).

\inputsnippets{folLogic/impE}

@@

\begin{project}[**]
  The type \texttt{SysPrf} has sort \texttt{Prop}, which prevent us from
extracting the underlying proof tree and its fringe from an hypothesis 
of the form $X\sdash f$. 
It would be nice (\emph{e.g.} for a better understanding of the proof of the deduction theorem) to be able to compute the  proof-tree built
by the proof of the deduction lemma. 
On a fresh branch of the project, please change the definition of
\texttt{SysPrf} and fix the errors this change could cause in the rest of the files. 
\emph{If ensuring compatibility with all the \texttt{Goedel} project is too long and/or difficult, you may just make the changes in separate modules with an ``informative'' \texttt{SysPrf} and limit the compatibility study  to the contents of basic modules like
\texttt{Deduction}, \texttt{folLogic}, etc.
Perhaps you will have to consider other implementation of finite sets of formulas (\emph{e.g.} lists).
}

\end{project}

@@

%\subsection{Applications of the Deduction Theorem}

The \emph{rule of implication introduction} is a trivial application of the deduction theorem.

\inputsnippets{folLogic/impI}
